%% The following is a directive for TeXShop to indicate the main file
%%!TEX root = diss.tex

\chapter{Abstract}

% The abstract is a concise and accurate summary of the scholarly work described in the document. 
% It states the problem, the methods of investigation, and the general conclusions, and should not contain tables, graphs, 
% complex equations, or illustrations. 
% There is a single scholarly abstract for the entire work, and it must not exceed 350 words in length.

Software developers traverse several commits and issues from issue tracking systems 
when exploring software revision history in order to unearth questions about the rationale behind presently written code.
\rev{This exploration results in a cognitive and temporal burden.
Challenges to exploring software revision history and obtaining code rationale information effectively
include overcoming the large volume of commits in a history, requiring the developer to filter
through trivial changes.}
Developers also must context switch between their \entity{IDE}s and a project's 
issue tracking system to locate code rationale information associated with each commit.
\rev{Thus, developers require more effective support for software revision history exploration
to better uncover code rationale information.}

\rev{We introduce Intelligent History, a plugin for the IntelliJ IDEA \entity{IDE}. 
Intelligent History uses commit history highlighting to reduce the search space of 
commits in a revision history, recommending to a developer which commits in a history might merit further investigation.}
Additionally, our approach minimizes the distance between a developer's \entity{IDE} and issues from an issue tracking system
by directly integrating issue information in the same context.

To evaluate the Intelligent History, we conducted a controlled laboratory study and recruited 10 software developers.
We asked two sets of questions related to the intent behind source code, requiring the participants to explore 
commit histories for two Java classes from the open-source Apache Kafka project.
We also conduct a semi-structured interview on the participants' experiences with examining issues and commits 
and their use of Intelligent History in the experiment.

The results from our analysis shows:
\rev{(1)} participants who used Intelligent History examined significantly
less commits than participants who did not use Intelligent History;
(2) direct integration of issue information in the \entity{IDE}
with Intelligent History might support developers who employ a commit history exploration approach
we describe as \textit{linear} or \textit{cyclic and backtracking} to contextualize
source code changes quickly and view slightly more issues than if they did not have
direct issue integration; and
\rev{(3)} there was overlap between at least half of the commits
that participants examined without Intelligent History and the commits that Intelligent History
highlighted.

% Consider placing version information if you circulate multiple drafts
% \vfill
% \begin{center}
% \begin{sf}
% \fbox{Revision: \today}
% \end{sf}
% \end{center}