%% The following is a directive for TeXShop to indicate the main file
%%!TEX root = diss.tex

\chapter{Preface}

The work presented in this thesis was conducted in the Software Practices Laboratory at the University of British Columbia, Point Grey campus.
All projects and associated methods were approved by the University of British Columbia's Research Ethics Board [certificate \#H22-01342]

I was the lead investigator, responsible for concept formation, implementation, data collection, analysis of the results, and manuscript composition.
Gail C. Murphy was the supervisory author on this project and was involved throughout concept formation and manuscript composition.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\endinput

The Preface must include a statement indicating the student's contribution to the following:

\begin{itemize}
    \item Identification and design of the research program,
    \item Performance of the various parts of the research, and
    \item Analysis of the research data.
    \item Certain additional elements may also be required, as specified below.
\end{itemize}

If any of the work presented in the thesis has led to any publications or submissions, all of these must be listed in the Preface. 
Bibliographic details should include the title of the article and the name of the publisher (ONLY if the article has been accepted or published), and the chapter(s) of the thesis in which the associated work is located.
If the work includes publications or material submitted for publication, the statement described above must detail the relative contributions of all collaborators and co-authors (including supervisors and members of the supervisory committee) and state the proportion of research and writing conducted by the student. For further details, see “Including Published Material in a Thesis or Dissertation”.
If the work includes other scholarly artifacts (such as film and other audio, visual, and graphic representations, and application-oriented documents such as policy briefs, curricula, business plans, computer and web tools, pages, and applications, etc.), all of these must be listed in the Preface (with bibliographical information, if applicable).
If ethics approval was required for the research, the Preface must list the Certificate Number(s) of the Ethics Certificate(s) applicable to the project.
In a thesis where the research was not subject to ethics review, produced no publications, and was designed, carried out, and analyzed by the student alone, the text of the Preface may be very brief. Samples are available on this website and in the University Library's online repository of accepted theses.

The content of the Preface must be verified by the student's supervisor, whose endorsement must appear on the final Thesis/Dissertation Approval form.